% University of New Haven Amateur Radio Club Consitution
% Copyright (C) 2023 KC1GCZ
%
% This program is free software: you can redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
%
% This program is distributed in the hope that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with this program.  If not, see <https://www.gnu.org/licenses/>.

\documentclass[a4paper,12pt]{article}
\usepackage{fullpage}
% \usepackage[utf8]{inputenc}
% \usepackage{extsizes}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{float}
\usepackage[margin=1.0in]{geometry}
\usepackage{enumitem}
\usepackage{cleveref}

\usepackage{draftwatermark}
\SetWatermarkText{DRAFT}
\SetWatermarkScale{5}

% \setlength{\parindent}{0em}
\renewcommand{\baselinestretch}{1.0}
\pagestyle{empty}

\setlist[enumerate]{leftmargin=*,align=left,label=\thesubsection.\arabic*.}

\crefname{section}{Section}{Sections}
\crefname{enumi}{Section}{Sections}

\title{UNewHaven Amateur Radio Club Consitution} 
\author{UNewHaven Amateur Radio Club Committee}
\date{Effective from 2024-x-x}

\begin{document}
\maketitle

\section{Preamble}
We, the undersigned, wishing to secure for ourselves the pleasures and benefits of an association of
persons commonly interested in Amateur Radio, constitute ourselves the \textit{University of New Haven's Amateur Radio Club}
of West Haven, CT and enact this constitution as our governing law. It shall be our purpose to further the exchange of
information and cooperation between members, to promote radio knowledge, fraternalism and
individual operating efficiency, and to so conduct club programs and activities as to advance the
general interest and welfare of Amateur Radio in the community.

\section{Purpose}
The purpose of this club is to promote intrest, research, and experimentation in wireless communication and Amateur Radio.

\section{Membership}
\begin{enumerate}[label=\thesection.\arabic*.]
  \item All Universtiy of New Haven members, including students, staff, and alumni interested in Amateur Radio communications shall be eligible for membership.
  \item Membership may not be denied because of race, creed, color, religion, gender, sexual orientation,
political affiliation, marital status or any other reason that would be biased or prejudicial.
\end{enumerate}


\section{Officers}

% \subsection{Officers}

\subsection{Officer's Eligibility}
\begin{enumerate}
  \item All Officers must be part time or full time students.
  \item The President and Vice President must be amateur radio operators with a valid license.
\end{enumerate}

\subsection{Duties of the Offices}
\begin{enumerate}
  \item \textbf{The President:} The President shall preside at all meetings, and conduct them according to the rules adopted. They shall enforce due observance of this Constitution and By-Laws; decide all questions of order; sign all official documents adopted by the club, and perform all other duties pertaining to the office of President.
  \item \textbf{The Vice President:} The Vice-President shall assume all the duties of the President in their absence. In addition, they shall organize club activities, plan and recommend contests for operating benefits, and advance club interest and activity as approved by the club.
  %They shall maintain close liaison with the local ARRL's local ARES ® Emergency Coordinator to further club participation in the Amateur Radio Emergency Service. ®
  \item \textbf{The Secretary:} The Secretary shall keep a record of the proceedings of all meetings, keep a roll of members, submit
membership applications, carry on all correspondence, read communications at each meeting, and
mail written meeting notices to each member. At the expiration of their term they shall turn over
all items belonging to the club to their successor.
  \item \textbf{The Treasurer:} The Treasurer shall receive and receipt for all monies paid to the club;
  keep an accurate account of all monies received and expended;
  keep track of all club owned equipments;
  pay no bills without proper authorization (by the club or its officers constituting a business committee). At the end of each quarter they shall submit an itemized statement of disbursements and receipts. At the end of their term they shall turn over everything in their possession belonging to the club to their successor.
\end{enumerate}

\subsection{Treasurer Role Sharing}
\begin{enumerate}
  \item The Treasurer's duties may be combined with the Secretary's, and thus both positions can be fullfilled by a single officer.
\end{enumerate}

\subsection{Office's Terms}
\begin{enumerate}
  \item A Term is one calendar year, starting from the last Sunday of August until the following year's last Sunday of August.
  \item An individual may not hold more than one office during the same term.
  \item An individual may not hold the same office for more than two terms.
\end{enumerate}

\subsection{Resignation}
\begin{enumerate}
  \item Any officer may resign their position in writing.
  \item All records and assets of the club will be turned over to the President or Vice President upon resignation.
\end{enumerate}

\subsection{Removal of Officers} \label{officer-removal}
\begin{enumerate}
  \item A written or typed petition signed from 3 members shall be presented to the President or Vice-President regarding the removal of an officer.
  \item The reason of removal must be stated clearly in the petition.
  \item The petition shall be acounced to all members during the next meeting
  \item An anouncement of the intent to present the petition shall be notified to all members no later than 3 days before the next meeting.
  \item Upon hearing the petition, there shall be an open discussion board.
  \item After the disucssion board, a vote (as per \cref{Voting}) shall occur. 
  \item Removal of an officer requires a 3/4 majority vote by all members.
\end{enumerate}

\subsection{Vacancies}
\begin{enumerate}
  \item A position may be vacant due to the resignation of an officer, the death of an officer, medical issues in which the officer is no longer able to act on their duties, or any unforseen causes.
  \item Any position that is vacant more than 1 month before the next election day (\cref{elec-time}) must be filled with a candiate with a Special Election per \cref{special-election}
\end{enumerate}

\section{Voting Process} \label{Voting}
\textit{This section is applicable to anytime the Members are required to vote on any manner. Any deviations from this section shall be mentioned when applicable.}
\subsection{The Vote}
\begin{enumerate}
  \item A vote can be casted by any Member of the club.
  \item \label{elec-anon} All votes are to be anonymized.
  \item For all in-person votes, at least 1/2 of all active members must be present. Otherwise, the vote will be turned into a asyncronous online vote.
  \item For all online voting, the voting poll must be open for at least 48 hours.
  \item For all online voting, the name or callsign of the voter must be recorded. The Secretary shall handle online voting. All online votes must be anonymized in the finally tally as per \cref{elec-anon}.
  \item The Secretary must tally the votes no later than 48 hours past the voting poll's closing time.
\end{enumerate}

\section{Election}

\subsection{Voting} \label{election-vote}
\begin{enumerate}
  \item \label{elec-time} Elections for new officers for shall be held on the first Monday of April. The election shall be for positions that will be held starting during the next Term.
  \item The meeting for the Election shall be anounced no later than 30 days from the election day.
  \item All members are elidgible to vote for a candidate for an Office.
  \item All Candiates and any other intrested members shall have 2 minutes to present their electibility to the rest of the members during the Election Meeting.
  \item No later than 48 hours after the Election Meeting, all candicates shall submit a written Statement of Candidancy to the Secretary.
  \item The Secretary shall setup an online vote for the candicates no later than 7 days from the Election Meeting's end time.
  \item The new Officers shall be anounced by online and in the next meeting following the vote tally by the President.
\end{enumerate}

\subsection{Candidates}
\begin{enumerate}
  \item All candidate must be members of the club prior to the first week of March.
  \item All members intrested in to be a candidate must communicate their intrested with the Secretary no later than 2 weeks prior to the Election Day.
\end{enumerate}

\subsection{Special Elections} \label{special-election}
\begin{enumerate}
  \item Special Elections are elections that occur at times other than regular elections per \cref{elec-time} for the sole purpose of filling in a vacant member.
  \item A Special Election must be planned by the Officers as soon as needed, no later than 3 days prior to the upcoming meeting. If the upcoming meeting is within 3 days of when a Special Election is needed, it will be pushed off to the next meeting.
  \item The Special Election shall be anounced prior to the next meeting, no later than 3 days prior to the upcoming meeting.
  \item Any member intrested in becoming a Special Candidate must make their intentions clear to the President or Vice-President prior to the Special Election meeting or during the start of it.
  \item The voting process will be the same as a regular election as per \cref{election-vote}
\end{enumerate}

\section{Meetings}
\begin{enumerate}[label=\thesection.\arabic*.]
  \item Meetings must be planned at least once a month by the Officers.
  \item All Meetings shall be anounced no later than 5 days prior to the Meeting.
  \item All Meeting's minutes shall be recorded by the Secretary.
  \item A Meeting shall have the following format, written chronologically:
  \begin{enumerate}
    \item The Secretary takes attendence of all present members.
    \item If there any Election or Removal Petition planned for this meeting, it shall be conducted.
    \item The President or Vice-President anounces any new acouncements regarding the Club.
    \item The Members will have a chance to speak of any concern, proposals, or whatever else they think is appropriate.
    \item The Meeting is ajourced by the President or Vice-President.
  \end{enumerate}
  \item A Meetings may be opted to be held online, either over a digital conference call or a digital chatting service.
\end{enumerate}

\section{Club Call Sign}
\begin{enumerate}[label=\thesection.\arabic*.]
  \item The Club may apply for a Club callsign as per CRF 47 Part 97.17.
  \item The Club may apply for a Vanity Club Callsign once approved as a Amatuer Club by the FCC and ARRL.
  \item The trustee of the club must be assigned by the President of the Club.
  \item The trustee must be in good standing with the club, an amatuer radio operator, and meets all FCC's requirements.
  \item The trustee may be revoked of their position in the same matter as an Officer, per \cref{officer-removal}.
\end{enumerate}

\section{Treasuries}
\begin{enumerate}[label=\thesection.\arabic*.]
  \item The Treasurer shall keep an active list of all club-owned equipment, tools, parts, and all other items.
  \item An item "owned" by the club can be a property of the University of New Haven, and the club as the designated user and manager of said item.
  \item The Treasurer shall keep track of the club's current funds.
  \item Any club purchases shall be done with the consensus of the President and Vice-President
\end{enumerate}

\section{Dissolution}
\begin{enumerate}[label=\thesection.\arabic*.]
  \item In the unfortunate event the club needs to be disolved, the club may be disolved by a 3/4 majority vote by all members.
  \item After the club's dissolution, all extra equipment and funds shall become property of the University of New Haven's Electrical and Computer Engineering department.
\end{enumerate}

\section{Constitutional and ByLaws Amendments and Changes}
\begin{enumerate}[label=\thesection.\arabic*.]
  \item Any proposal to the consitution should be mentioned at the end of the Meeting period by any member.
  \item The proposed change should be discussed during the meeting when mentioned.
  \item If half of the members present during the meeting vote on the proposed change, the amendment shall be considered a Proposed Amendment
  \item The Secretary shall draft up the official changed based off the voted Proposed Amendment and present it during the next meeting
  \item An anoucment shall be made by the Officers to all members no less than 1 week prior to the next meeting regarding the Constitution Amendment.
  \item During the next meeting, the Officers shall present the offical Proposed Amendment to all members.
  \item The Proposed Amendment must be approved by a 2/3 majority vote for it to become part of the consitution.
  \item The updated Constitution shall be emailed to \textit{studentactivities@newhaven.edu}
\end{enumerate}

\end{document} 
